Twisted 11-dimensional supergravity, I

### 2021-08-04 draft.tex
merge

\subsubsection{}
We set up some notations and conventions in the context of complex geometry. 
Let $V$ be a holomorphic vector bundle on a complex manifold $X$. 
If $j$ is an integer, we let $\Omega^{0,j}(X, V)$ denote the space of anti-holomorphic Dolbeault forms of type $j$ on with values in $V$.
The $\dbar$ operator for $V$ is $\dbar \colon \Omega^{0,j}(X, V)\to \Omega^{0,j+1}(X)$ defines the Dolbeault complex of $V$
\[
  \Omega^{0,\bu}(X, V) = \left(\Omega^{0,j}(X, V)[-j] \; , \; \dbar\right) .
\]
This is a free resolution for the sheaf of holomorphic sections of $V$.

@@

Let $X$ be a Calabi--Yau manifold of dimension $d$. 
Let $\PV^{k,\bu}(X)$ denote the Dolbeault complex of the holomorphic vector bundle $\wedge^k \T_X$. 
In particular, $\PV^{k,j}(X)$ is the space of smooth sections of the bundle $\wedge^j \T_X^* \otimes \wedge^k \T_X$. 
With this notation, the dg Lie algebra in \eqref{eqn:cplx1} is $\PV^{1,\bu}(X) \oplus \PV^{0,\bu}(X)[-1]$ with differential $\dbar + \div$.

Introduce a formal parameter $u$ of cohomological degree $+2$ and consider the complex 
\beqn\label{eqn:pv1}
\PV^{\bu,\bu} (X) [[u]] [1]
\eeqn
with differential $\dbar + u \div$ which we will often denote just by $Q_{KS}$ and refer to as the linear BRST differential. 
With our conventions, notice that $u^l \PV^{k,j}(X)$ sits in cohomological degree $2l +k + j - 1$.

The Schouten--Nijenhuis bracket 
\[
[-,-]_{NS} \colon \PV^{k,j} (X) \times \PV^{p,q} (X) \to \PV^{p+k-1,j+q} (X) 
\]
extends $u$-linearly to endow \eqref{eqn:pv1} with the structure of a dg Lie algebra.
We refer to this as the Kodaira--Spencer, or strict, dg Lie algebra structure.
We refer to the further cohomological shift 
\[
\cE_{KS} = \PV^{\bu,\bu} (X) [[u]] [2]
\]
as the space of fields of Kodaira--Spencer theory.

Notice that the complex resolving divergence-free vector fields \eqref{eqn:cplx1} sits inside $\cE_{KS} [-1]$ as a sub dg Lie algebra as $\PV^{1,\bu}(X) \oplus u \PV^{0,\bu}(X)[1]$.

@@

\begin{thm}[\cite{CLbcov1}]
The BCOV action 
\[
I_{BCOV} \in \oloc \left(\cE_{KS} \right) 
\]
satisfies the classical master equation 
\[
Q_{KS} I_{BCOV} + \frac12 \left\{I_{BCOV}, I_{BCOV}\right\}_c = 0 .
\]
In other words, $I_{BCOV}$ determines a Maurer--Cartan element in the dg Lie algebra $\oloc(\cE)[-2d+5]$.
\end{thm}

@@

Consider the following cochain complex $\cE$:
\beqn\label{eqn:E}
\begin{tikzcd}
\ul{-1} & \ul{0} & \cdots & \ul{d-5} & \ul{d-4} &   \\
\PV^{1,\bu} \ar[r,"\div"] & \PV^{0,\bu} & \cdots & & \\
& & & \Omega^{0, \bu} \ar[r,"\del"] & \Omega^{1, \bu} 
\end{tikzcd}
\eeqn
We will write the fields using the notation
\begin{align*}
(\mu, \nu) & \in \Pi \PV^{1,\bu}(X)[1] \oplus \PV^{0,\bu}(X) \\
(\beta, \gamma) & \in \Omega^{0,\bu}(X)[d-5] \oplus \Omega^{1,\bu}(X) [d-4].
\end{align*}

@@

Define the pairing 
\[
\omega \colon \cE_c \times \cE \to \cE [??] 
\]
by the formula $\int^\Omega \gamma \vee \mu + \int^\Omega \beta \nu.$

@@

Define the map of cochain complexes
\[
\Phi \colon \cE \to \til{\cE}_{KS}
\]
by the formulas
\[
\Phi (\mu,\nu) = \mu + u \nu,\qquad \Phi(\beta, \gamma) = \div \left( \gamma \vee \Omega^{-1} \right)  .
\]
In the last expression we have used the isomorphism
\[
(-) \vee \Omega^{-1} \colon \Omega^{1,\bu} \xto{\cong} \PV^{d-1,\bu} 
\]
so that $\div(\gamma \vee \Omega^{-1}) \in \PV^{d-2,\bu} \subset \til{\cE}$.

\begin{prop}
\label{prop:pot}
The map $\Phi \colon  \cE \to \til{\cE}_{KS}$ intertwines the linear BRST differentials and the shifted Poisson bivectors $\Phi_*\Pi = \til{\Pi}_{KS}$. 
In particular, it defines a map of dg Lie algebras
\[
\Phi^* \colon \big(\oloc(\cE_{KS}),\{-,-\}_c, Q_{KS} \big) \to \big(\oloc(\cE),\{-,-\}, Q \big)
\]
\end{prop}

@@

\begin{cor}
The BCOV action $\til{I}_{BCOV}$ restricts along $\Phi$ to a solution of the classical master equation for $\cE$:
\begin{align*}
I & = \Phi^* \til{I}_{BCOV} \\
Q I + \frac12 \{I,I\} & = 0 .
\end{align*} 
\end{cor}

@@

>>>>

\subsubsection{}
\label{sec:divfree}
We set up some notations and conventions in the context of complex geometry. 
Let $V$ be a holomorphic vector bundle on a complex manifold $X$. 
If $j$ is an integer, we let $\Omega^{0,j}(X, V)$ denote the space of anti-holomorphic Dolbeault forms of type $j$ on with values in $V$.
The $\dbar$ operator for $V$ is $\dbar \colon \Omega^{0,j}(X, V)\to \Omega^{0,j+1}(X)$ defines the Dolbeault complex of $V$
\[
  \Omega^{0,\bu}(X, V) = \left(\Omega^{0,j}(X, V)[-j] \; , \; \dbar\right) .
\]
This is a free resolution for the sheaf of holomorphic sections of $V$.

@@

Suppose $X$ be a Calabi--Yau manifold of dimension $d$. 
Let $\PV^{k,\bu}(X)$ denote the Dolbeault complex of the holomorphic vector bundle $\wedge^k \T_X$; we will omit $X$ in this section and write $\PV^{k,\bu}$ for simplicity.
In particular, $\PV^{k,j}$ is the space of smooth sections of the bundle $\wedge^j \T_X^* \otimes \wedge^k \T_X$. 
With this notation, the dg Lie algebra in \eqref{eqn:cplx1} is $\PV^{1,\bu} \oplus \PV^{0,\bu}[-1]$ with differential $\dbar + \div$.

Introduce a formal parameter $u$ of cohomological degree $+2$ and consider the complex 
\beqn\label{eqn:pv1}
\PV^{\bu,\bu} [[u]] [1]
\eeqn
with differential $\dbar + u \div$ which we will often denote just by $Q_{KS}$ and refer to as the linear BRST differential. 
With our conventions, notice that $u^l \PV^{k,j}$ sits in cohomological degree $2l +k + j - 1$.

The Schouten--Nijenhuis bracket 
\[
[-,-]_{NS} \colon \PV^{k,j} \times \PV^{p,q} \to \PV^{p+k-1,j+q} 
\]
extends $u$-linearly to endow \eqref{eqn:pv1} with the structure of a dg Lie algebra.
We refer to this as the Kodaira--Spencer, or strict, dg Lie algebra structure.
We refer to the further cohomological shift 
\[
\cE_{KS} = \PV^{\bu,\bu} [[u]] [2]
\]
as the space of fields of Kodaira--Spencer theory.

Notice that the complex resolving divergence-free vector fields \eqref{eqn:cplx1} sits inside $\cE_{KS} [-1]$ as a sub dg Lie algebra as $\PV^{1,\bu} \oplus u \PV^{0,\bu}[1]$.

@@

\begin{thm}[\cite{CLbcov1}]
The BCOV action 
\[
I_{BCOV} \in \oloc \left(\cE_{KS} \right) 
\]
satisfies the classical master equation 
\[
Q_{KS} I_{BCOV} + \frac12 \left\{I_{BCOV}, I_{BCOV}\right\}_c = 0 .
\]
In other words, $I_{BCOV}$ determines a Maurer--Cartan element in the dg Lie algebra $\oloc(\cE_{KS})[-2d+5]$.
\end{thm}

@@

Consider the following cochain complex $\cE_{pot}$:
\beqn\label{eqn:E}
\begin{tikzcd}
\ul{-1} & \ul{0} & \cdots & \ul{d-5} & \ul{d-4} &   \\
\PV^{1,\bu} \ar[r,"\div"] & \PV^{0,\bu} & \cdots & & \\
& & & \Omega^{0, \bu} \ar[r,"\del"] & \Omega^{1, \bu} 
\end{tikzcd}
\eeqn
We will write the fields using the notation
\begin{align*}
(\mu, \nu) & \in \Pi \PV^{1,\bu}(X)[1] \oplus \PV^{0,\bu}(X) \\
(\beta, \gamma) & \in \Omega^{0,\bu}(X)[d-5] \oplus \Omega^{1,\bu}(X) [d-4].
\end{align*}

@@

Define the pairing 
\[
\omega \colon \cE_{pot,c} \times \cE_{pot} \to \CC [??] 
\]
by the formula $\int^\Omega \gamma \vee \mu + \int^\Omega \beta \nu.$

@@

Define the map of cochain complexes
\[
\Phi \colon \cE_{pot} \to \til{\cE}_{KS}
\]
by the formulas
\[
\Phi (\mu,\nu) = \mu + u \nu,\qquad \Phi(\beta, \gamma) = \div \left( \gamma \vee \Omega^{-1} \right)  .
\]
In the last expression we have used the isomorphism
\[
(-) \vee \Omega^{-1} \colon \Omega^{1,\bu} \xto{\cong} \PV^{d-1,\bu} 
\]
so that $\div(\gamma \vee \Omega^{-1}) \in \PV^{d-2,\bu} \subset \til{\cE}_{KS}$.

\begin{prop}
\label{prop:pot}
The map $\Phi \colon  \cE_{pot} \to \til{\cE}_{KS}$ intertwines the linear BRST differentials and the shifted Poisson bivectors $\Phi_*\Pi = \til{\Pi}_{KS}$. 
In particular, it defines a map of dg Lie algebras
\[
\Phi^* \colon \big(\oloc(\cE_{KS}),\{-,-\}_c, Q_{KS} \big) \to \big(\oloc(\cE_{pot}),\{-,-\}, Q \big)
\]
\end{prop}

@@

\begin{cor}
The BCOV action $\til{I}_{BCOV}$ restricts along $\Phi$ to a solution of the classical master equation for $\cE_{pot}$:
\begin{align*}
I_{pot} & = \Phi^* \til{I}_{BCOV} \\
Q I_{pot} + \frac12 \{I_{pot},I_{pot}\} & = 0 .
\end{align*} 
\end{cor}

@@

Define the action by the group $\CC^\times$ on $\cE$ as follows. 
Declare $\mu, \nu$ have $\CC^\times$ weight zero and $\beta,\gamma$ have $\CC^\times$ weight $+1$. 
The linear BRST operator is of weight zero and the pairing $\omega$ is of weight $+1$. 
Thus, the shifted Poisson bracket $\{-,-\}$ is of $\CC^\times$ weight $-1$.

\begin{lem}
The restricted action $I_{pot} = \Phi^* I_{BCOV}$ has $\CC^\times$ weight $+1$. 
In particular, the non-linear BRST operator 
\[
\delta_{pot} = Q_{pot} + \{I_{pot},-\}
\]
is $\CC^\times$ weight zero.
\end{lem}

Consider the cochain complex $\left(\oloc(\cE_{pot}) \, , \, \delta_{pot} \right)$ of all local functionals equipped with the non-linear BRST differential $\delta_{pot}$. 
The $\CC^\times$ weight zero subcomplex is 
\[
\big(\oloc(\cE_{pot})^{(0)} \, , \, \delta_{pot} \big) = \big(\oloc(\cE_0) \, , \, \delta_{pot} \big) 
\]
where $\cE_0 = \PV^{1,\bu}[1] \oplus \PV^{0,\bu}$ is the subcomplex of the fields $\cE_{pot}$ consisting of just the $\mu$ and $\nu$ fields.

\begin{prop}
\label{prop:Linfty}
The differential $\delta_{pot}$ acting on the weight zero fields induces a local $L_\infty$ algebra structure on the complex of vector bundles 
\[
\cE_0 [-1] = \PV^{1,\bu} \oplus \PV^{0,\bu}[-1]
\]
with $[-]_1 = \dbar + \div$. 
Furthermore, this $L_\infty$ algebra structure is equivalent to the strict dg Lie algebra structure on the resolution of divergence-free vector fields defined in \S \ref{sec:divfree}. 
\end{prop}

The previous proposition characterizes the $L_\infty$ model for divergence-free vector fields that we will use to define the 11-dimensional theory of twisted supergravity. 
Hereon, we denote by $\cL_0 = \cE_0[-1]$ this local $L_\infty$ algebra.

We can unpack Proposition \ref{prop:Linfty} to describe the $L_\infty$ structure on $\cL_0$ explicitly. 
Recall we have two types of elements $\mu \in \PV^{1,\bu}$ and $\nu \in \PV^{0,\bu}[-1]$. 
The first few nonzero brackets are
\begin{align*}
[\mu]_1 & = \dbar \mu + \div \mu \\
[\mu_1,\mu_2]_2 & = \div (\mu_1 \mu_2) \\
[\nu, \mu_1,\mu_2]_3 & = \div(\nu \mu_1 \mu_2) \\
[\nu_1,\nu_2, \mu_1,\mu_2]_4 & = \# \div(\nu_1 \nu_2 \mu_1 \mu_2).
\end{align*}
For $k \geq 2$ the general formula for the $k$-ary bracket is 
\[
[\nu_1,\nu_2, \ldots, \nu_{k-2}, \mu_1,\mu_2]_{k} = \# \div(\nu_1 \cdots \nu_k \mu_1 \mu_2) .
\]

\subsection{The 11-dimensional theory}
